### 2019-04-02 1_introduction.tex
Small tweaks and edits.

One approach to comparing the performance of different systems has
focused on the development of \emph{proxy-} or
\emph{mini-apps}. Because they distill the structure of a larger
application, mini-apps can provide insight
without the expense of developing a full-blown
application. However, despite the name, our experience is that
mini-apps still requite significant investment to develop, especially
to the level of quality needed for useful benchmarking. In many cases,
the effort to tune for performance exceeds the effort to develop the
mini-app in the first place. As a result, implementations of mini-apps
often do not reach the level of maturity required to compare
systems. Indeed, there are few such published studies that involve
more than a handful of systems.

@@

To address the second issue and isolate the contribution of the programming model's runtime system
to application performance, we introduce a new metric called
\emph{minimum effective task granularity} (METG). Intuitively,
METG(50\%) is the smallest application task granularity which can be
executed while maintaining at least 50\% computational efficiency,
meaning that the application achieves at least 50\% of peak
performance on a given machine. METG captures the essence of what is important in a weak
or strong scaling study, the behavior at the limit of scalability. For
weak scaling, METG(50\%) corresponds directly to the smallest problem
size that can be weak scaled with 50\% efficiency. For strong scaling,
METG(50\%) can be used to compute the scale at which performance can
be expected to dip below 50\% efficiency.

>>>>

One approach to comparing the performance of different systems has
focused on the development of \emph{proxy-} or
\emph{mini-apps}. Because they distill the structure of a larger
application, mini-apps can provide insight
without the expense of developing a full-blown
application. However, despite the name, our experience is that
mini-apps still requite significant investment to develop, especially
to the level of quality needed for useful benchmarking. In many cases,
the effort to tune for performance exceeds the effort to develop the
mini-app in the first place. As a result, implementations of mini-apps
often do not reach the level of maturity required to compare
systems. Indeed, there are few such published studies
that involve more than a handful of systems~\cite{LULESH13}.

@@

To address the second issue and isolate the contribution of the programming model's runtime system
to application performance, we introduce a new metric called
\emph{minimum effective task granularity} (METG). Intuitively,
METG(50\%) is the smallest application task granularity which can be
executed while maintaining at least 50\% efficiency,
meaning that the application achieves at least 50\% of peak
performance (e.g., FLOPS) 
on a given machine. METG captures the essence of what is important in a weak
or strong scaling study, the behavior at the limit of scalability. For
weak scaling, METG(50\%) corresponds directly to the smallest problem
size that can be weak scaled with 50\% efficiency. For strong scaling,
METG(50\%) can be used to compute the scale at which performance can
be expected to dip below 50\% efficiency.

### 2019-04-02 4_implementation.tex
apply some of George's comments
Small tweaks and edits.

Data in PaRSEC is stored in a built-in matrix data structure with a 2D
block cyclic distribution. Tiles of the matrix are distributed across nodes in pre-defined patterns,
and can be passed to tasks on other nodes, but
can only be written on the node where the data is originally
allocated. In our Task Bench implementation, each task writes to a
tile as output, and these tiles are passed as inputs to the
subsequent sets of tasks. As in the OmpSs and OpenMP implementations,
the task launch code uses a switch statement as the PaRSEC API assumes
tasks have a fixed number of dependencies.

@@

StarPU~\cite{StarPU11} is a task-based system that supports a \emph{sequential task flow} (STF)
programming model similar to PaRSEC's DTD. Our Task Bench implementation in
StarPU is very similar to PaRSEC, including the use of a switch
statement to handle dynamic numbers of task dependencies, and manual
elision of tasks on unrelated nodes to provide horizontal scalability.
A simplified version of the 2D block cyclic matrix from the Chameleon 
project~\cite{Chameleon} is used to describe the data produced by tasks in 
our Task Bench implementation.

>>>>

Task Bench uses a 2D block cyclic data distribution provided by PaRSEC. Tiles of data are 
distributed across nodes in pre-defined patterns,
and can be passed to tasks on other nodes, but
can only be written on the node where the data is originally
allocated. In our Task Bench implementation, each task writes to a
tile as output, and these tiles are passed as inputs to the
subsequent sets of tasks. As in the OmpSs and OpenMP implementations,
the task launch code uses a switch statement as the PaRSEC API assumes
tasks have a fixed number of dependencies.

@@

StarPU~\cite{StarPU11} is a task-based system that supports a \emph{sequential task flow} (STF)
programming model similar to PaRSEC's DTD. Our Task Bench implementation in
StarPU is very similar to PaRSEC, including the use of a switch
statement to handle dynamic numbers of task dependencies, and manual
elision of tasks on unrelated nodes to provide horizontal scalability.
We use a simplified version of the 2D block cyclic data distribution from the Chameleon 
project~\cite{Chameleon}.
